---
title: "Visualization of COVID19 Data in Bicol"
author: "Ateneo REGIS Hub"
date: "July 17, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Visualization of COVID19-related Data from Bicol Region and Naga City, Camarines Sur, Philippines  



*Data sources used to make the plots are official press releases of DOH CHD - Bicol and official releases from the COVID Tracker of the Local Government of Naga.*


The following interactive plot shows the **Covid19-positive individuals and their contacts** in  **Bicol Region** as of **July 16, 2020**.  

**Use your mouse to zoom in to particular cases, see details, and look into connections.** 


```{r, comment= FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

library(dplyr)
library(data.table)
library(lubridate)
library(reshape2)
library(ggplot2)
library(EpiEstim)
library(epicontacts)
library(googlesheets4)


bicol3 <- (read_sheet("https://docs.google.com/spreadsheets/d/1wBC115kZxPbphHgf39so5r5XR2pibbWDV-soXxGiS64/edit#gid=0")
)

```

```{r, comment= FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

linelist <- cbind(bicol3[, 1:5], bicol3[, 10:12], bicol3[, 17])

contacts <- bicol3[, 15:21]


y2 <- make_epicontacts(linelist = linelist,
                      contacts = contacts,
                      directed = TRUE )



plot(y2, selector = TRUE)
``` 


## Time Varying R in Bicol Region as of **July 16, 2020**

The following figure shows the output plots: **Epidemic Curve, Estimated R, and Explored Serial Interval Distribution **

```{r, comment= FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

library(EpiEstim)
library(ggplot2)
library(readxl)


dailycases <- as.data.table(read_excel("EpiEstim-Cori-et-al-Time-varying-R-BICOL.xls", sheet = 2))


dailycases[, Date := ymd(dailycases[, Date])]

dailycases <- dailycases %>% 
                rename(
                  I = `Total Cases`
                      )

dailycases <- dailycases[, 2:3]


res_parametric_si <- estimate_R(dailycases, 
                                method="parametric_si",
                                config = make_config(list(
                                  mean_si = 3.96, 
                                  std_si = 4.75))
)


plot(res_parametric_si, legend = FALSE) 
```  


###References:

**R Core Team (2017). R: A language and environment for statistical computing. R  Foundation for Statistical Computing, Vienna, Austria. URhttps://www.R-project.org/**

**packages used: dplyr, data.table, lubridate, reshape2, ggplot2, EpiEstim, epicontacts, googlesheets4, readxl**

**Help us improve our viz. Send a pull request at [link](https://github.com/shanebimeda/regishub)**  



H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New York, 2016    
   
Matt Dowle and Arun Srinivasan (2019). data.table: Extension of `data.frame`. R package version 1.12.8. https://CRAN.R-project.org/package=data.table  

Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2020). dplyr: A Grammar of Data Manipulation. R package version 1.0.0.https://CRAN.R-project.org/package=dplyr  

Anne Cori (2020). EpiEstim: Estimate Time Varying Reproduction Numbers from Epidemic Curves. R package version 2.2-3. https://CRAN.R-project.org/package=EpiEstim  

Hadley Wickham and Jennifer Bryan (2019). readxl: Read Excel Files. R package version 1.3.1. https://CRAN.R-project.org/package=readxl    

VP Nagraj, Thibaut Jombart, Nistara Randhawa, Bertrand Sudre, Finlay Campbell and Thomas Crellen (2017). epicontacts: Handling, Visualisation and Analysis of Epidemiological Contacts. R package version 1.1.0. https://CRAN.R-project.org/package=epicontacts  
  
Garrett Grolemund, Hadley Wickham (2011). Dates and Times Made Easy with lubridate. Journal of Statistical Software, 40(3), 1-25. URL http://www.jstatsoft.org/v40/i03/  

Hadley Wickham (2007). Reshaping Data with the reshape Package. Journal of Statistical Software, 21(12), 1-20. URL http://www.jstatsoft.org/v21/i12/  

Jennifer Bryan (2020). googlesheets4: Access Google Sheets using the Sheets API V4. R package version 0.2.0. https://CRAN.R-project.org/package=googlesheets4  

Yihui Xie (2020). knitr: A General-Purpose Package for Dynamic Report Generation in R. R package version 1.29.  

Yihui Xie (2015) Dynamic Documents with R and knitr. 2nd edition. Chapman and Hall/CRC. ISBN 978-1498716963  

Yihui Xie (2014) knitr: A Comprehensive Tool for Reproducible Research in R. In Victoria Stodden, Friedrich Leisch and Roger D. Peng, editors, Implementing Reproducible Computational Research. Chapman and Hall/CRC. ISBN 978-1466561595  


